Multi-line Intensity Mapping

### 2019-07-15 paper/ms.tex
Citations, small changes

\subsection{Intrinsic Line Emission}\label{ssec:line_emission}
The average intensity of an arbitrary line is calculated according
to the simple model of \citet{2016ApJ...825..143L}, which is based upon
\citet{2011ApJ...741...70L} and {\bf Pullen 2013}. The details are laid out in
Appendix~\ref{app:co_int}, but in brief the model assumes a {\bf Schechter
1976} form for the star formation rate function and a linear relationship
between a halo's luminosity and its star formation rate with constants of
proportionality from \citet{2010JCAP...11..016V}.

@@

For the cross-spectrum between two lines $i$ and $j$, we assume that
\beq\label{eq:cross_spec}
P_{i,j}(k, \mu, z) = r_{i,j}(k, z) \sqrt{P_{i,i}(k, \mu, z) P_{j,j}(k, \mu, z)}
\eeq

@@

While in principle one can extract $\bi$ and $\Ii$ independently due to the
$\mu$-dependence of the Kaiser effect, there are a number of observational
challenges \citep{2019arXiv190500209C}. We will therefore only consider the constraints
that can be placed on the product of the two, i.e., $B_i \equiv \bi \Ii$. The
previous Fisher matrix can be converted to the equivalent one for constraints
on $B_i$, $F'$, by the following relation \citep[e.g.][]{2009arXiv0906.4123C}:
\beq\label{eq:fisher_transform}
F' = M^{\mathsf{T}} F M\text{,}
\eeq
where
\beq\label{eq:trans_matrix}
M_{ij} = \frac{\partial \theta_i}{\partial B_j}\text{.}
\eeq

>>>>

\subsection{Intrinsic Line Emission}\label{ssec:line_emission}
The average intensity of an arbitrary line is calculated according
to the simple model of \citet{2016ApJ...825..143L}, which is based upon
\citet{2011ApJ...741...70L} and \citet{2013ApJ...768...15P}. The details are laid out in
Appendix~\ref{app:co_int}, but in brief the model assumes a \citet{1976ApJ...203..297S} form for the star formation rate function and a linear relationship
between a halo's luminosity and its star formation rate with constants of
proportionality from \citet{2010JCAP...11..016V}.

@@

For the cross-spectrum between two lines $i$ and $j$, we assume that
\beq\label{eq:cross_spec}
P_{i,j}(k, \mu, z) = r_{i,j}(k, z) \sqrt{P_{i,i}(k, \mu, z) P_{j,j}(k, \mu, z)}\text{,}
\eeq
where $r_{i,j}$ is the cross-correlation coefficient between line $i$ and $j$.
We will only consider scales where $r_{i,j} = 1$.

@@

While in principle one can extract $\bi$ and $\Ii$ independently due to the
$\mu$-dependence of the Kaiser effect, there are a number of observational
challenges \citep{2019arXiv190500209C}. We will therefore only consider the constraints
that can be placed on the product of the two, i.e., $B_i \equiv \bi \Ii$. The
previous Fisher matrix can be converted to the equivalent one for constraints
on $B_i$, $F'$, by the following relation \citep[e.g.][]{2009arXiv0906.4123C}:
\beq\label{eq:fisher_transform}
F' = M^{\text{T}} F M\text{,}
\eeq
where
\beq\label{eq:trans_matrix}
M_{ij} = \frac{\partial \theta_i}{\partial B_j}\text{.}
\eeq

\subsection{Noise Components}\label{ssec:noise}
We describe the implementation of each noise component.

\subsubsection{Interloping and Extraloping Lines}\label{sssec:interlopers}
